I/O simulation extension for SimGrid framework

### 2020-04-21 paper_io_sim.tex
Update
paper outline

\documentclass[11pt, a4paper]{article}

@@

\begin{abstract}

\end{abstract}

	\section{Introduction}

	\section{Related Work}

		\subsection{Page cache}
			\begin{itemize}
				\item What is page cache? How it works.
				\item Effects and importance of page cache
			\end{itemize}

		\subsection{ Page cache replacement policies}
			\begin{itemize}
				\item Introduce some proposed strategies.
				\item Some pros and cons of each algorithm if possible.
			\end{itemize}

		\subsection{Implementation in Linux}
			\begin{itemize}
				\item Details of the implemented strategy in Linux.
				\item Reason for this to be implemented. (implementation complexity, effectiveness, overhead, etc)
			\end{itemize}

		\subsection{Simulators}
		Compare pros and cons of some simulators: SimGrid, GridSim (accuracy, simulation time, usability).

		\subsection{Our conclusion}

@@

			\begin{itemize}
				\item Objective: Add capability to simulate memory read/write, the impact of page cache on I/O in SimGrid.
				\item Approach: generalize dirty data, dirty ratio, cache eviction strategy implemented in Linux. 
			\end{itemize}

@@

			\item Ability of the model to generalize trends of memory usage and disk throughput.

@@

	\section{Discussion}

>>>>

\documentclass[conference]{IEEEtran}

@@

\begin{abstract}
	\begin{itemize}
		\item The I/O bottleneck in HPC and the need of conducting HPC experiments.
		\item Difficulties in HPC experiments and simulation frameworks.
		\item Advantages of SimGrid, the missing of the ability to simulate page cache, the goal of this paper.
	\end{itemize}
\end{abstract}

	\section{Introduction}
		\begin{itemize}
			\item Role of high performance computing nowadays and the demand of HPC experiments.
			\item Difficulties in conducting high performance computing experiments and the need of simulation frameworks.
			\item Existing methods, simulators, simulation frameworks. 
			\item The advantages of SimGrid compared to others. The missing of the ability to simulate page cache in SimGrid.
			\item The objective of the paper: Add capability to simulate memory read/write, the impact of page cache on I/O in SimGrid.
		\end{itemize}
	\section{Related Work}

		\subsection{Page cache}
			\begin{itemize}
				\item What is page cache? How it works. Effects and importance of page cache
				\item Introduce some existing strategies.
				\item Current implementation in Linux and some reasons for this to be implemented (implementation complexity, effectiveness, overhead, etc)
			\end{itemize}

		\subsection{Simulators}
		Discuss some ecisting methods, simulation frameworks to conduct HPC experiments. Compare pros and cons (accuracy, simulation time, usability) of some simulators (SimGrid, GridSim) .

@@

			\begin{itemize}
				\item Approach: generalize dirty data, dirty ratio, cache eviction strategy implemented in Linux. 
				\item Some implemented details of the simulator in SimGrid.
			\end{itemize}

@@

			\item Ability of the model to generalize trends seen in memory (amount of dirty data, page cache) and disk throughput.

@@

	\section{Discussion and Future Work}
